\section{Change Operating System of Control Unit}

\subsection{Objective}
To simplify the work experience, a change in the main operating system on the control unit was performed. The original OS was Windows 10, and the target OS was Ubuntu 24.04 LTS.

\subsection{Procedure}
To perform the reboot of the OS, the following steps were taken:

\subsection{Preparation: USB Stick and ISO Image}
\begin{itemize}
    \item USB Stick with 128GB.
    \item Download the Ubuntu ISO: \href{https://ubuntu.com/download}{https://ubuntu.com/download}.
\end{itemize}

\subsection{Step 1: Create a Bootable USB Stick (For Windows Users)}
Download and Start Rufus (on Windows)
\begin{itemize}
    \item Download Rufus: \href{https://rufus.ie/de/}{https://rufus.ie/de/}.
\end{itemize}

\subsubsection{Configure Rufus Settings}
\begin{itemize}
    \item \textbf{Device:} Select the USB stick in the “Device” dropdown menu.
    \item \textbf{Boot Selection:} Click “SELECT” and choose the Ubuntu ISO file downloaded earlier.
    \item \textbf{Partition Scheme:}
    \begin{itemize}
        \item Select \textbf{GPT} when using UEFI.
        \item Select \textbf{MBR} when using an older BIOS or UEFI with CSM (Compatibility Support Module).
    \end{itemize}
    \item \textbf{Target System:}
    \begin{itemize}
        \item UEFI (non-CSM) for newer devices.
        \item BIOS (or UEFI-CSM) for older devices.
    \end{itemize}
    \item \textbf{File System:} FAT32.
\end{itemize}

\subsubsection{Start the Process}
\begin{itemize}
    \item Wait for the process to complete.
\end{itemize}

\subsection{Step 2: Boot Ubuntu from the USB Stick}
\begin{itemize}
    \item Plug in the USB stick and restart your laptop.
    \item Open the Boot Menu:
    \begin{itemize}
        \item Use one of the following keys: F12, F10, Esc, or Del.
    \end{itemize}
    \item Select the USB stick as the boot device to start Ubuntu.
\end{itemize}

\subsection{Step 3: Install Ubuntu}
Start the Installation
\begin{itemize}
    \item Follow the installation guide.
\end{itemize}

Choose Installation Type
\begin{itemize}
    \item Example: \textbf{“Erase disk and install Ubuntu”} to remove Windows and use only Ubuntu.
\end{itemize}

Advanced Features (Optional)
\begin{itemize}
    \item Configure as needed.
\end{itemize}

Confirm Installation
\begin{itemize}
    \item Wait for the process to complete.
\end{itemize}

\subsection{Step 4: After Installation}
\begin{itemize}
    \item Remove the USB stick and restart.
    \item Use Ubuntu.
\end{itemize}